%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setlength{\parindent}{0pt}
\setlength{\textheight}{22cm}
\setlength{\parskip}{0.2cm}

% Para aumentar o espaçamento entre as linhas
\linespread{1.2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{Lamport94}
\bibitem[Malik Ghallab, Dana Nau, Paolo Traverso; 2004]{AUTOMATEDPLANNING} %Nau2004
	Malik Ghallab, Dana Nau, Paolo Traverso 
	\newblock {\em Automated Planning}.
	ISBN: 1558608567 - Morgan Kaufmann (May 3, 2004).

\bibitem[Claus, Jacques Wainer; 2005]{SUBSTITUICAOREATIVA} %Castro2005
    Claus de Castro Aranha, Jacques Wainer
    \newblock {\em Sistema de Substituição: uma técnica reativa para 
      auto-reparo e auto-diagnóstico de planos}.
    Master Thesis - POLI-USP - March,2005.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARECE QUE NAO ESTA SENDO UTILIZADO NO TEXTO!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem[Alexander Nareyek; 1998]{PLANDYNREALTIME}
    Alexander Nareyek 
    \newblock {\em A Planning Model for Agents in Dynamic and Uncertain 
      Real-Time Enviroments}.
    AIPS Workshop on Integrating Planning, Scheduling and Execution in 
    Dynamic and Uncertain Environments, pages 7-14, 1998.

\bibitem[R. Krogt; 2005]{PLANREPAIR} %Roman2005
	R. Krogt, M. Weerdt  
	\newblock {\em Plan Repair as an Extension of Planning}.
	International Conference on Automated Planning and Scheduling
	- ICAPS 2005.

\bibitem[S. Kambhampati; 1997]{REFINAMENTPLANNING} %Kambhampati1997
  S. Kambhampati
  \newblock {\em Refinement planning as a unifying framework
  for plan synthesis}. 
  AI Magazine 18(2):67-97 (1997).

\bibitem[Bernhard Nebel, Jana Koehler; 1993]{PLANMODXPLANGEN} %Bernhard1993
	Bernhard Nebel, Jana Koehler 
	\newblock {\em Plan Modification versus Plan Generation: A
	Complexity-Theoretic Perspective}
	International Joint Conferences on Artificial Intelligence
	- JCAI 1993: 1436-1444.

\bibitem[Stuart Russell, Peter Norvig; 2004]{AIMA} %Russell2002
	Stuart Russell, Peter Norvig  
	\newblock {\em AI: A Modern Approach}.
	ISBN 8535211772 - Elsevier (2004).% - pág 365-404.

\bibitem[R. Krogt, M. Weerdt; 2004]{TWOFACESPLANREPAIR} %Roman2004
	R. Krogt, M. Weerdt 
	\newblock {\em The Two Faces of Plan Repair}.
	Belgian-Dutch Conference on Artificial Intelligence 
	- BNAIC 2004.

\bibitem[W. Cushing, S. Kabhampati; 2005]{NEWREPLANNING} %Kabhampati2005
    Wiliam Cushing, Subarao Kabhampati  
    \newblock {\em Replanning: a New Perspective}.
	International Conference on Automated Planning and Scheduling 
	- ICAPS 2005.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARECE QUE NAO ESTA SENDO UTILIZADO NO TEXTO!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem[Alexander Nareyek; 2003]{DYNWORLDS} %Nareyek2003
	Alexander Nareyek 
	\newblock {\em Planning in Dynamic Worlds: More Than External 
	  Events}.
	IJCAI-2003 Workshop on Agents and Automated Reasoning, 30-35.

\bibitem[F. Tonidandel; 2003]{PLANBASEADOEMCASOS} %Tonidandel2003
  Flavio Tonidandel
  \newblock {\em Desenvolvimento e Implementação de um Sistema de Planejamento
  Baseado em Casos}.
  Tese de Doutorado em Engenharia - POLI-USP 2003.

\bibitem[R. Krogt, A. Bos, C. Witteveen; 2001]{FRAGMENTLIBRARIES} %Roman2001
	R. Krogt, A. Bos, C. Witteveen
	\newblock {\em Plan fragment libraries}. 
	Belgium-Netherlands Artificial Intelligence Conference 
	- BNAIC 2001.

\bibitem[A. Botea, M. Muller, J. Schaeffer; 2004]{GENERATIONMACROACTIONS} %Adi2004
	Adi Botea, Martin Muller, Jonathan Schaeffer
	\newblock {\em Using component abstraction for automatic 
	  generation of macro-actions}. 
	International Conference on Automatic Planning and Scheduling 
	- ICAPS 2004

\bibitem[H. L. S. Younes, R. G. Simmons; 2003]{VHPOP} %Younes2003
	Younes, H. L. S., Simmons, R. G. 
	\newblock {\em VHPOP: Vesatile heuristic partial order planner}.
	Jair 20:405-430 (2003)

\bibitem[Gerevini, A., Serina, I.; 2000]{GPG} %Gerevini2000
	Gerevini, A., Serina, I.
	\newblock {\em Fast plan adaptation through planning graphs: 
	Local and systematic  search  tecniques}.
	In Proc. of the Fifih Int. Conf. On AI Planning Systems (AIPS - 2000), 112-121. Menlo Pak, CA: AAAI Press. 

\bibitem[Smith, D. E., Weld, D. S.; 1998]{CONFORMANTGRAFPLAN} %Smith1998
	Smith, D. E., Weld, D. S.
	\newblock {\em Conformant Grafplan}.
	In Proc. of the Fifteenth Natonal Conference on Artificial Intelligence - AAAI 1998

\bibitem[Warren, D. H. D.; 1976]{WARPLANC} %Warren1976
	Warren, D. H. D.
	\newblock {\em Generating conditional plans and programs}.
	In Proc. of the AISB Summer Conference - 1976

\bibitem[Draper, D., Hanks, S., Weld, D. S.; 1994]{CBURIDAN}
	Draper, D., Hanks, S., Weld, D. S.
	\newblock {\em Probabilistic planning with information gathering and contingent execution}.
	In Proc. of the Second International Conference on AI Planning Systems - 1994

\bibitem[Hansen, E. Zilberstein, S.; 2001]{LAO} %Hansen2001
	Hansen, E. Zilberstein, S.
	\newblock {\em LAO*: a heuristic search algorithm that finds solutions with loops}.
	In Proc. Artificial Intelligence - 2001

\bibitem[Bonet, B. Geffner, H.; 2000]{PLANNINGINCOMPLETEINFORMATION} %Bonet2000
	 Bonet, B. Geffner, H.
	\newblock {\em Planning with incomplete information as heuristic search in belief space}.
	International Conference on Artificiall Intelligence Planning and Scheduling - 2000

\bibitem[Wilkins, D. E.; 1988]{SIPE-1988} %Wilkins1988
	 Wilkins, D. E.
	 \newblock {\em Pratical Planning: Extending the AI Planning Paradigm}.

\bibitem[Wilkins, D. E.; 1990]{SIPE-1990} %Wilkins1990
	 Wilkins, D. E.
	 \newblock {\em Can AI planners solve practical problems?}.
	 Computational Intelligence - 1990

\bibitem[Ambros-Ingerson J., Steel S.; 1988]{IPEM} %Ambros1988
	 Ambros-Ingerson J., Steel S.
	 \newblock{\em Integratirig planning, execution and monitoring}.
	 In Proc. of the Seventh National Conference on Artificial Intelligence - AAAI 1988

\bibitem[Blum, A. L., Furst, M. L.; 1997]{GRAFPLAN} %Blum1997
         Blum, A. L., Furst, M. L.
	 \newblock{\em Fast Planning through planning graph analysis}.
	 Artificial Intelligence 90:281-300 - 1997

\bibitem[Boella, G., Damiano, R.; 2002]{REPLAN} %Boella2002
   Boella, G., Damiano, R.
	 \newblock{\em A replanning algorithm for a reactive agent architecture}.
	 In Atificial Intelligence: Methodology, Systems, and Applications (LLNCS 2443), 183-192. Springer Verlag - 2002.

\bibitem[Weiss, G.; 1999]{MULTIAGENT} %Weiss1999
  Weiss, G.
  \newblock{\em Multiagent system}.
  MIT Press, Cambrige, Massachusetts.

\bibitem[Erol, K., Hendler, J., Nau, D. S.; 1994]{HTN} %Erol1994
         Erol, K.; Hendler, J.; Nau, D. S. 1994
	 \newblock{\em Semantics for hierarchical task network planning}.
	 Technical Report CS-TR-3239, UNIACS-TR-94-31, Computer Science, University of Maryland - 1994.

\bibitem[Drabble B., Dalton J., Tate A.; 1997]{OPLAN} %Drabble1997
         Drabble B., Dalton J., Tate, A.
	 \newblock{\em Repairing plans on the fly}.
	 In Proc. Of thr NASA Workshop on planning and Scheduling for Space, Oxnad, CA - 1997.

\bibitem[Wang, X., Chien, S.; 1997]{REPLANNING_HTN} %Wang1997
         Wang, X., Chien, S.
	 \newblock{\em Replanning using hierarchical task network and operator-based planning}.
	 Technical report, Jet Propulsion Laboratory Nasa.


\bibitem[S. Hanks, D. S. Weld; 1995]{SPA}
         S. Hanks, D. S. Weld
	 \newblock{\em A Domain-Independent Algorithm for Plan Adaptation}.
	 Journal of Artificial Intelligence Research, Vol 2, (1995), 319-360 - 1995.


\end{thebibliography}
