\chapter{Questionário sobre Boas e Más Práticas}

\begin{center}
\textbf{Android Good \& Bad Practices}

Help Android Developers around the world in just 15 minutes letting us know what you think about good \& bad practices in Android native apps. Please, answer in portuguese or english.

Hi, my name is Suelen, I am a Master student researching code quality on native Android App's Presentation Layer. Your answers will be kept strictly confidential and will only be used in aggregate. I hope the results can help you in the future. If you have any questions, just contact us at suelengcarvalho@gmail.com.
\end{center}

\textbf{Questions about Demographic \& Background.} Tell us a little bit about you and your experience with software development. All questions throught this session were mandatory.
\begin{enumerate}
	\item What is your age? (One choice beteen 18 or younger, 19 to 24, 25 to 34, 35 to 44, 45 to 54, 55 or older and I prefer not to answer)
	\item Where do you currently live? 
	\item Years of experience with software development? (One choice between 1 year or less, one option for each year between 2 and 9 and 10 years or more)
	\item What programming languages/platform you consider yourself proficient? (Multiples choices between Swift, Javascript, C\#, Android, PHP, C++, Ruby, C, Python, Java, Scala, Objective C, Other)
	\item Years of experience with developing native Android applications? (One choice between 1 year or less, one option for each year between 2 and 9 and 10 years or more)
	\item What is your last degree? (One choice between Bacharel Student, Bacharel, Master, PhD and Other)
\end{enumerate}

\textbf{Questions about Good \& Bad Practices in Android Presentation Layer.} We want you to tell us about your experience. For each element in Android Presentation Layer, we want you to describe good \& bad practices (all of them!) you have faced and why you think they are good or bad. With good \& bad practices we mean anything you do or avoid that makes your code better than before. If you perceive the same practice in more than one element, please copy and paste or refer to it. All questions throught this session were not mandatory.
\begin{enumerate}

	\item \textbf{Activities} An activity represents a single screen.
	\begin{itemize}
		\item Do you have any good practices to deal with Activities? 
		\item Do you have anything you consider a bad practice when dealing with Activities?
	\end{itemize}

	\item \textbf{Fragments} A Fragment represents a behavior or a portion of user interface in an Activity. You can combine multiple fragments in a single activity to build a multi-pane UI and reuse a fragment in multiple activities.
	\begin{itemize}
		\item Do you have any good practices to deal with Fragments?
		\item Do you have anything you consider a bad practice when dealing with Fragments?
	\end{itemize}

	\item \textbf{Adapters} An adapter adapts a content that usually comes from model to a view like put a bunch of students that come from database into a list view.
	\begin{itemize}
		\item Do you have any good practices to deal with Adapters?
		\item Do you have anything you consider a bad practice when dealing with Adapters?
	\end{itemize}

	\item \textbf{Listeners} An event listener is an interface in the View class that contains a single callback method. These methods will be called by the Android framework when the View to which the listener has been registered is triggered by user interaction with the item in the UI.
	\begin{itemize}
		\item Do you have any good practices to deal with Listeners?
		\item Do you have anything you consider a bad practice when dealing with Listeners?
	\end{itemize}

	\item \textbf{Layouts Resources} A layout defines the visual structure for a user interface.
	\begin{itemize}
		\item Do you have any good practices to deal with Layout Resources?
		\item Do you have anything you consider a bad practice when dealing with Layout Resources?
	\end{itemize}

	\item \textbf{Styles Resources} A style resource defines the format and look for a UI.
	\begin{itemize}
		\item Do you have any good practices to deal with Styles Resources?
		\item Do you have anything you consider a bad practice when dealing with Styles Resources?
	\end{itemize}

	\item \textbf{String Resources} A string resource provides text strings for your application with optional text styling and formatting. It is very common used for internationalizations.
	\begin{itemize}
		\item Do you have any good practices to deal with String Resources?
		\item Do you have anything you consider a bad practice when dealing with String Resources?
	\end{itemize}

	\item \textbf{Drawable Resources} A drawable resource is a general concept for a graphic that can be drawn to the screen.
	\begin{itemize}
		\item Do you have any good practices to deal with Drawable Resources?
		\item Do you have anything you consider a bad practice when dealing with Drawable Resources?
	\end{itemize}
\end{enumerate}

\textbf{Last thoughts} Only 3 more final questions.
\begin{enumerate}
	\item Are there any other *GOOD* practices in Android Presentation Layer we did not asked you or you did not said yet?
	\item Are there any other *BAD* practices in Android Presentation Layer we did not asked you or you did not said yet?
	\item Leave your e-mail if you wish to receive more information about the research or participate in others steps.
\end{enumerate}




